Interactive Visualization for System Log Analysis

### 2013-12-17 paper/paper.tex
Updated results and style and format

\begin{CRcatlist}
  \CRcat{I.3.3}{Computer Graphics}{Three-Dimensional Graphics and Realism}{Display Algorithms}
  %CRcat{I.3.7}{Computer Graphics}{Three-Dimensional Graphics and Realism}{Radiosity};
\end{CRcatlist}

\keywordlist

@@

%% Required for all content.

\copyrightspace

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.9\textwidth]{images/ganglia.png}
    \caption{Screenshot of Ganglia (image courtesy of Wikipedia). This information shows various metrics for a single node.}
    \label{fig:ganglia}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.9\textwidth]{images/rrdtool.png}
    \caption{A screenshot of RRDtool attempting to coherently display a lot of information to the user, but ending up extremely cluttered.\protect\footnotemark}
    \label{fig:rrdtool}
\end{figure*}
\footnotetext{\url{http://oss.oetiker.ch/rrdtool/gallery/index.en.html}}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\columnwidth]{images/screenshot_controls.png}
    \caption{User controls}
    \label{fig:ss_controls}
\end{figure}

@@

\subsection{Anomaly Detection}
We set the metric for anomaly detection as follow: How many clusters are required until anomalous
node in its own cluster? In the best case of this scenario the number of cluster always should be
two if there is only one type of anomalies at a time.

In Figure~\ref{fig:anomaly} you can see the performance of our anomaly detection and it shows that
our system can tell anomalies such as a failing or slow node under the interference like random
noises. The system works well even when 50\% of the data is garbage, i.e., randomly generated logs.

\begin{figure}[p]
    \centering
    \includegraphics[width=1.0\columnwidth]{images/anomaly.pdf}
    \caption{Anomaly detection}
    \label{fig:anomaly}
\end{figure}

If we were able to find a ground-truth log file with labeled anomalies, we could compare our error
rates to those presented in papers by Wei Xu et al. Unfortunately, we couldn't find any publicly
accessible log database.

\subsection{Timing Information}
We ran on 500,000 messages per node and on average 30MB of data were sent to the HTTP Server per
node. Visualization took on the client side so the computation cost of visualization doesn't slow
down the server. In Figure~\ref{fig:timings} you can see basic timing information of our system.

\begin{figure}[p]
    \centering
    \includegraphics[width=1.0\columnwidth]{images/timing.pdf}
    \caption{Timing information}
    \label{fig:timings}
\end{figure}

@@

\section*{Acknowledgements}
The authors appreciate Ling Huang for his helpful advices and Sean Arietta for providing the log
data gathered from his research project.

>>>>

@@

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.85\textwidth]{images/ganglia.png}
    \caption{Screenshot of Ganglia (image courtesy of Wikipedia). This information shows various metrics for a single node.}
    \label{fig:ganglia}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.85\textwidth]{images/rrdtool.png}
    \caption{A screenshot of RRDtool attempting to coherently display a lot of information to the user, but ending up extremely cluttered.\protect\footnotemark}
    \label{fig:rrdtool}
\end{figure*}
\footnotetext{\url{http://oss.oetiker.ch/rrdtool/gallery/index.en.html}}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\columnwidth]{images/screenshot_controls.png}
    \caption{The configuration options available to the user via our web framework. The user can change these options at interactive rates.}
    \label{fig:ss_controls}
\end{figure}

@@

The success of our system depends on three axes: clustering performance, speed, and user friendliness.
The third axis is the most difficult to evaluate, but we currently have one user of the system who is excited to use and improve it.
We formally evaluate the other two axes here.

\subsection{Anomaly Detection}
\label{subsec:results:anomaly}
The metric of success for anomaly detection is as follow: assuming only one node is anomalous, how many clusters are required until that node is in its own cluster?
The best-case scenario is two clusters: one for each of the $n-1$ well-performing nodes, and another for the anomalous node.

We simulate five experiments on a seven node cluster using six nodes of real data and one node of simulated anomalous data.
The five anomalies tested are:
\begin{enumerate}
\item
\textbf{Failed node}

One node fails when the algorithm is 80\% to completion, and all other nodes run to completion.
\item
\textbf{Node 5\% slower}

One node runs 5\% slower than the speed of the other nodes
\item
\textbf{Node 1\% slower}

One node runs 1\% slower than the speed of the other nodes
\item
\textbf{50\% of log is junk}

Half of the messages in each log file are random, both in time and in value. One node is still 5\% slower. Can the anomalous node be detected?
\item
\textbf{99\% of log is junk}

Only one out of every hundred messages is real. One node is still 5\% slower. Can the anomalous node be detected? Note that the filesize here is bloated to 100 times the actual log data.
\end{enumerate}

Figure~\ref{fig:anomaly} shows the performance of our clustering on each of the above tests.
Most of the clustering successfully detects an anomaly with just two clusters.
The two failure cases are a 1\% slowdown of a node, and when 99\% of the log is not useful information and information is outputted at random times.
We assume these cases are rare, and are satisfied with successfully clustering a 5\% slowdown and 50\% junk log data.

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{images/anomaly.pdf}
    \caption{Results for anomaly detection via clustering. The x axis shows different simulation evaluations; the yaxis is the number of clusters required until the anomalous node is in its own cluster. Two clusters is the best-case scenario. See Section~\ref{subsec:results:anomaly} for a description of each of the simulation numbers.}
    \label{fig:anomaly}
\end{figure}

We would like to eventually compare our algorithm with the results of Xu and collaborators \cite{Xu09}.
Unfortunately, all of their results used private proprietary logs, so we could not do a direct comparison.

\subsection{Timing}
\label{subsec:results:timing}
Our log files had over 500,000 messages per node.
After compression, 30MB of data were sent to the master server per node.
The visualization was served to the client via an HTTP server, and all javascript visualizations were computed client-side, so the only cost of visualization is generating and transferring the data.

Figure~\ref{fig:timings} shows basic timing information of our system.
From this, it is clear that the per-node cost is small: less than two seconds to compute features per-node.
This data is then passed on to the master node, which preprocesses everything and prepares to send it to the client via HTTP.
This preprocessing is the bottleneck in our unoptimized implementation.
Finally, when the user changes the parameters with the web interface, recomputing the clusters takes an average of $.2$ seconds.

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{images/timing.pdf}
    \caption{Timing information. The first column is the per-node log parsing and feature extraction. The second column is the work the master server must do. The last column is the time a user must wait until an updated visualization is displayedafter changing the configuration. See Section \ref{subsec:results:timing} for more details.}
    \label{fig:timings}
\end{figure}

@@

\section*{Acknowledgements}
The authors would like to thank Ling Huang for helpful discussions and Sean Arietta for providing us with the log data gathered from his research project.
